Community Detection Methods for Generalized Random Dot Product Graphs

### 2021-05-29 proposal/proposal.tex
updated slides

Graph and network data, in which samples are represented not as a collection of feature vectors but as relationships between pairs of observations, are increasingly widespread in various fields ranging from sociology to computer vision. One common goal of analyzing graph data is community detection or graph clustering, in which the graph is partitioned into disconnected subgraphs in an unsupervised yet meaningful manner (e.g., by optimizing an objective function or recovering unobserved labels). Because traditional clustering techniques were developed for data that can be represented as vectors, they cannot be applied directly to graphs. In this research, we investigate the use of a family of spectral decomposition based approaches for community detection in block models, first by demonstrating how under the Generalized Random Dot Product Graph framework, all graphs generated by block models can be represented as feature vectors, then by proposing clustering methods for these feature vector representations and deriving the asymptotic properties of these methods.

@@

Graph and network data have become increasingly widespread in various
fields including sociology, neuroscience, biostatistics, and computer
science. This has resulted in various challenges for researchers who
rely on traditional statistical and machine learning methods, many of
which are incompatible with graph data and instead require the data to
exist as feature vectors in Euclidean space. This includes graph
clustering and community detection, which are often the goal of data
analysis on graphs and networks. Common clustering methods typically
involve calculating some central or representative point for each
cluster around which the data belonging to that cluster lie (e.g.,
Lloyd's algorithm for \(K\)-means clustering \cite{1056489}, Gaussian
Mixture Models \cite{doi:10.1198/016214502760047131}). Because these
methods involve computing summary statistics within each cluster, such
as the sample average, they cannot be applied directly to graphs,
necessitating methods for transforming the graph data into feature
vectors.

One family of methods for unifying graph community detection with
traditional clustering techniques is Spectral Clustering
\cite{DBLP:journals/corr/abs-0711-0189}, which involves embedding the
graph into Euclidean space, followed by applying a popular clustering
algorithm such as \(K\)-means clustering. The Random Dot Product Graph
(RDPG) \cite{10.1007/978-3-540-77004-6_11} and Generalized Random Dot
Product Graph (GRDPG) \cite{rubindelanchy2017statistical} models take
this further by explicitly constructing generative models for graphs
involving latent vectors in Euclidean space. In such a model, each
vertex has a corresponding vector in latent space, and the edge
probabilities between pairs of vertices is computed by operations on
corresponding pairs of latent vectors. A community detection algorithm
motivated by this may involve learning the latent positions given an
observed graph and then learning the community labels given the latent
positions.

The aim of our research is to develop consistent community detection
techniques under the RDPG and GRDPG frameworks. First, we explore
existing generative graph models with underlying community structures
that can be inferred by connecting these models to the RDPG or GRDPG. In
particular, we use the connection between the Popularity Adjusted Block
Model \cite{307cbeb9b1be48299388437423d94bf1} and the GRDPG to motivate
two community detection methods. Then we explore other latent structures
or mixture distributions in the latent space that induce graphs for
which consistent community detection is possible.

@@

Let \(G = (V, E)\) be an undirected, unweighted graph with no self-loops
and \(n\) vertices. Denote \(A \in \{0, 1\}^{n \times n}\) as the
adjacency matrix for \(G\) such that \(A_{ij} = 1\) if there exists an
edge between vertices \(i\) and \(j\) and \(A_{ij} = 0\) otherwise.
Because \(G\) is symmetric and contains no self-loops,
\(A_{ij} = A_{ji}\) and \(A_{ii} = 0\) for \(i, j \in [n]\). We further
restrict our analyses to independent Bernoulli graphs. Let
\(P \in [0, 1]^{n \times n}\) be a symmetric matrix of edge
probabilities. Graph \(G\) is sampled from \(P\) by drawing
\(A_{ij} \stackrel{\text{ind}}{\sim}\text{Bernoulli}(P_{ij})\) for each
\(1 \leq i < j \leq n\) (\(A_{ji} = A_{ij}\) and \(A_{ii} = 0\)). We
denote \(A \sim \text{BernoulliGraph}(P)\) as graph with adjacency
matrix \(A\) sampled from edge probability matrix \(P\) in this manner.
If each vertex has a hidden label in \([K]\), they are denoted as
\(z_1, ..., z_n\). Finally, we denote
\(X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}\)
as the sample \(x_1, ..., x_n \in \mathbb{R}^d\).

@@

Generative models for independent Bernoulli graphs involve defining the
edge probability matrix \(P\) whose \(ij\)\textsuperscript{th} entry is
the probability of an edge between vertices \(i\) and \(j\) for each
\(i, j \in [n]\). In order to motivate community detection methods, we
restrict the generative model such that for each pair of vertices
\((i, j)\), the probability of an edge between the vertices \(P_{ij}\)
depends in some way on their labels \(z_i\) and \(z_j\).

One such model is the Stochastic Block Model (SBM)
\cite{doi:10.1080/0022250X.1971.9989788}: Given \(K\) communities and
each vertex belonging to one community, the SBM restricts \(P\) to
\(K (K + 1) / 2\) unique entries such that \(P_{ij} = p_{z_i z_j}\)
where \(p_{kl} = p_{lk}\) is the probability of an edge between each
vertex in community \(k\) to each vertex in community \(l\). The
homogeneous SBM further restricts \(P\) to two unique entries:
\(P_{ij} = p\) if \(z_i = z_j\) and \(P_{ij} = q\) otherwise. Several
generalizations of the SBM have been introduced since, including the
Degree Corrected Block Model (DCBM) \cite{Karrer_2011} and the
Popularity Adjusted Block Model (PABM)
\cite{307cbeb9b1be48299388437423d94bf1}. Like the SBM, these models
involve imposing some restriction on \(P\) based on community labels
(and possibly other factors).

@@

If $A \sim \text{GRDPG}_{p, q}(X)$, then let $A = V \Lambda V^\top$ be the approximate spectral decomposition of $A$ corresponding to the $p$ most positive and $q$ most negative eigenvalues of $A$ and their corresponding eigenvectors. Then the rows of $V |\Lambda|^{1/2}$ and $V$ are the scaled and unscaled ASE of $A$ respectively.
\end{definition}

\citet{athreya2017statistical} showed that under mild conditions, if
\((A_n, X_n) \sim \text{RDPG}(F, n)\) and \(\hat{X}_n\) is the scaled
ASE of \(A_n\), for some sequence of orthogonal matrices \(W_n\),

@@

where \(Q_n\) is a sequence of matrices in \(\mathbb{O}(p, q)\), the
indefinite orthogonal group of order \(p, q\).

It is straightforward to show that all Bernoulli graphs with positive
semidefinite \(P\) are special cases of the RDPG, which is a special
case of the GRDPG, and all graphs generated by \(P\) regardless of
positive semidefiniteness are special cases of the GRDPG. This includes
the SBM, DCBM, and PABM. In the following example, we show that under
the RDPG framework, the latent configuration that induces the SBM takes
on a very particular form.

@@

where the first $n_1$ rows are $\begin{bmatrix} \sqrt{p} & 0 \end{bmatrix}$ and the next $n_2$ rows are $\begin{bmatrix} \sqrt{r^2 / p} & \sqrt{q - r^2 / p} \end{bmatrix}$. This is shown by reconstructing $P$ as $P = X X^\top$.
\end{example}

The ASE of the assortative SBM consists of points in \(\mathbb{R}^K\)
that lie near one of \(K\) centers, depending on the community label,
leading to ASE followed by \(K\)-means clustering (or similar, e.g.,
GMM) as a consistent community detection algorithm \cite{lyzinski2014}.
A similar result can be shown for the DCBM and PABM but with different
structures in the ASE.

@@

\begin{definition}[Popularity Adjusted Block Model]
\label{pabm}
Let $P \in [0, 1]^{n \times n}$ be a symmetric edge probability matrix for a 
set of $n$ 
vertices, $V$. Each vertex has a community label $1, ..., K$, and the rows and 
columns of $P$ are arranged by community label such that $n_k \times n_l$ block 
$P^{(kl)}$ describes the edge probabilities between vertices in communities 
$k$ and $l$ ($P^{(lk)} = (P^{(kl)})^\top$). 
Let graph $G = (V, E)$ be an undirected, unweighted graph such 
that its corresponding adjacency matrix $A \in \{0, 1\}^{n \times n}$ is a 
realization of $\text{Bernoulli}(P)$, i.e., 
$A_{ij} \stackrel{\text{ind}}{\sim}\text{Bernoulli}(P_{ij})$ for $i > j$ 
($A_{ij} = A_{ji}$ and $A_{ii} = 0$).

@@

It is straightforward to show that the PABM, as well as all graphs such
that the adjacency matrix is drawn such that
\(A_{ij} \stackrel{\text{ind}}{\sim}Bernoulli(P_{ij})\), is a special
case of the GRDPG. It can also be shown that the latent positions of the
PABM under the GRDPG framework consists of \(K\) \(K\)-dimensional
subspaces in \(\mathbb{R}^{K^2}\). While there is no unique latent
configuration \(X\) such that \(X X^\top = P\), the edge probability
\(P\) for the PABM, they all have this subspace structure, and one in
particular consists of \emph{orthogonal} subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent
configuration for a \(K\)-community PABM under the GRDPG framework
consists of vectors in \(\mathbb{R}^{K^2}\) such that each community
corresponds to a \(K\)-dimensional subspace and each subspace is
orthogonal to the others.

>>>>

Graph and network data, in which samples are represented not as a collection of feature vectors but as relationships between pairs of observations, are increasingly widespread in various fields ranging from sociology to computer vision. One common goal of analyzing graph data is community detection or graph clustering, in which the graph is partitioned into disconnected subgraphs in an unsupervised yet meaningful manner (e.g., by optimizing an objective function or recovering unobserved labels). Because traditional clustering techniques were developed for data that can be represented as vectors, they cannot be applied directly to graphs. In this research, we investigate the use of a family of spectral decomposition based approaches for community detection in block models (random graph models with inherent community structure), first by demonstrating how under the Generalized Random Dot Product Graph framework, all graphs generated by block models can be represented as feature vectors, then applying clustering methods for these feature vector representations, and finally deriving the asymptotic properties of these methods.

@@

Graph and network data have become increasingly widespread in various
fields including sociology, neuroscience, biostatistics, and computer
science. This has resulted in various challenges for researchers who
rely on traditional statistical and machine learning methods, many of
which are incompatible with graph data and instead require the data to
exist as feature vectors in Euclidean space. This includes graph
clustering and community detection, which are often the goal of data
analysis on graphs and networks. Common clustering methods typically
involve calculating some central or representative point for each
cluster around which the data belonging to that cluster lie (e.g.,
Lloyd's algorithm for \(K\)-means clustering \cite{1056489}, Gaussian
Mixture Models \cite{doi:10.1198/016214502760047131}). Because these
methods involve computing summary statistics within each cluster, such
as the sample average, they cannot be applied directly to graphs,
necessitating methods for transforming the graph data into feature
vectors if they are to be used.

One family of methods for unifying graph community detection with
traditional clustering techniques is Spectral Clustering
\cite{DBLP:journals/corr/abs-0711-0189}, which involves embedding the
graph into Euclidean space, followed by applying a popular clustering
algorithm such as \(K\)-means clustering. The Random Dot Product Graph
(RDPG) \cite{10.1007/978-3-540-77004-6_11} and Generalized Random Dot
Product Graph (GRDPG) \cite{rubindelanchy2017statistical} models take
this further by explicitly constructing generative models for graphs via
latent vectors in Euclidean space. In such a model, each vertex has a
corresponding vector in latent space, and the edge probabilities between
pairs of vertices are computed by operations on the corresponding pairs
of latent vectors. A community detection algorithm motivated by this may
involve learning the latent positions given an observed graph and then
learning the community labels given the latent positions.

The aim of our research is to develop consistent community detection
techniques under the RDPG and GRDPG frameworks. First, we explore
existing generative graph models with underlying community structures
(Block Models) that can be inferred by connecting these models to the
RDPG or GRDPG. In particular, we use the connection between the
Popularity Adjusted Block Model \cite{307cbeb9b1be48299388437423d94bf1}
and the GRDPG to motivate two community detection methods. Then we
explore other latent structures or mixture distributions in the latent
space that induce graphs for which consistent community detection is
possible.

@@

Let \(G = (V, E)\) be an undirected, unweighted graph with no self-loops
and \(n\) vertices. Denote \(A \in \{0, 1\}^{n \times n}\) as the
adjacency matrix of \(G\) such that \(A_{ij} = 1\) if there exists an
edge between vertices \(i\) and \(j\) and \(A_{ij} = 0\) otherwise.
Because \(G\) is symmetric and contains no self-loops,
\(A_{ij} = A_{ji}\) and \(A_{ii} = 0\) for \(i, j \in [n]\). We further
restrict our analyses to independent Bernoulli graphs. Let
\(P \in [0, 1]^{n \times n}\) be a symmetric matrix of edge
probabilities. Graph \(G\) is sampled from \(P\) by drawing
\(A_{ij} \stackrel{\text{ind}}{\sim}\text{Bernoulli}(P_{ij})\) for each
\(1 \leq i < j \leq n\) (\(A_{ji} = A_{ij}\) and \(A_{ii} = 0\)). We
denote \(A \sim \text{BernoulliGraph}(P)\) as graph with adjacency
matrix \(A\) sampled from edge probability matrix \(P\) in this manner.
If each vertex has a hidden label in \([K]\), they are denoted as
\(z_1, ..., z_n\). Finally, we denote
\(X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}\)
as the sample \(x_1, ..., x_n \in \mathbb{R}^d\).

@@

Generative models for independent Bernoulli graphs involve defining the
edge probability matrix \(P\) whose \(ij\)\textsuperscript{th} entry is
the probability of an edge between vertices \(i\) and \(j\) for each
\(i, j \in [n]\). In order to motivate community detection methods, we
restrict the generative model such that for each pair of vertices
\((i, j)\), the probability of an edge between the vertices \(P_{ij}\)
depends in some way on their labels \(z_i\) and \(z_j\). Such models are
called Block Models.

One type of Block Model is the Stochastic Block Model (SBM)
\cite{doi:10.1080/0022250X.1971.9989788}: Given \(K\) communities and
each vertex belonging to one of the \(K\) communities, the SBM restricts
\(P\) to \(K (K + 1) / 2\) unique entries such that
\(P_{ij} = p_{z_i z_j}\) where \(p_{kl} = p_{lk}\) is the probability of
an edge between each vertex in community \(k\) to each vertex in
community \(l\). The homogeneous SBM further restricts \(P\) to two
unique entries: \(P_{ij} = p\) if \(z_i = z_j\) and \(P_{ij} = q\)
otherwise. Several generalizations of the SBM have been introduced
since, including the Degree Corrected Block Model (DCBM)
\cite{Karrer_2011} and the Popularity Adjusted Block Model (PABM)
\cite{307cbeb9b1be48299388437423d94bf1}. Like the SBM, these models
involve imposing some restriction on \(P\) based on community labels
(and possibly other factors).

@@

If $A \sim \text{GRDPG}_{p, q}(X)$, then let $A \approx V \Lambda V^\top$ be the approximate spectral decomposition of $A$ corresponding to the $p$ most positive and $q$ most negative eigenvalues of $A$ and their corresponding eigenvectors. Then the rows of $V |\Lambda|^{1/2}$ and $V$ are the scaled and unscaled ASE of $A$ respectively.
\end{definition}

\citet{athreya2017statistical} showed that under mild conditions, if
\((A_n, X_n) \sim \text{RDPG}(F, n)\) and \(\hat{X}_n\) is the scaled
ASE of \(A_n\), for some sequence of orthogonal matrices \(\{W_n\}\),

@@

where \(\{Q_n\}\) is a sequence of matrices in \(\mathbb{O}(p, q)\), the
indefinite orthogonal group of order \(p, q\).

It is straightforward to show that all Bernoulli graphs with positive
semidefinite \(P\) are special cases of the RDPG, which is a special
case of the GRDPG, and all Bernoulli Graphs generated by \(P\)
regardless of positive semidefiniteness are special cases of the GRDPG.
This includes the SBM, DCBM, and PABM. In the following example, we show
that under the RDPG framework, the latent configuration that induces the
SBM takes on a very particular form.

@@

where the first $n_1$ rows are $\begin{bmatrix} \sqrt{p} & 0 \end{bmatrix}$ and the next $n_2$ rows are $\begin{bmatrix} \sqrt{r^2 / p} & \sqrt{q - r^2 / p} \end{bmatrix}$. This is shown by reconstructing $P$ as $P = X X^\top$. Thus the SBM is equivalent to a RDPG with the latent configuration of two point masses, one for each community. 
\end{example}

The ASE of the assortative SBM consists of points in \(\mathbb{R}^K\)
that lie near one of \(K\) centers, depending on the community label,
leading to ASE followed by \(K\)-means clustering (or similar, e.g.,
GMM) as a consistent community detection algorithm \cite{lyzinski2014}.
A similar result has been shown for the DCBM \cite{lyzinski2014}, and
our work extends this to the PABM.

@@

\begin{definition}[Popularity Adjusted Block Model]
\label{pabm}
Let $P \in [0, 1]^{n \times n}$ be a symmetric edge probability matrix for a 
set of $n$ 
vertices, $V$. Each vertex has a community label $1, ..., K$, and the rows and 
columns of $P$ are arranged by community label such that $n_k \times n_l$ block 
$P^{(kl)}$ describes the edge probabilities between vertices in communities 
$k$ and $l$ ($P^{(lk)} = (P^{(kl)})^\top$). 
Let graph $G = (V, E)$ be an undirected, unweighted graph such 
that its corresponding adjacency matrix $A \in \{0, 1\}^{n \times n}$ is a 
realization of $\text{BernoulliGraph}(P)$.

@@

It is straightforward to show that the PABM (as well as all Bernoulli
Graphs) is a special case of the GRDPG. It can also be shown that the
latent positions of the PABM under the GRDPG framework consists of \(K\)
\(K\)-dimensional subspaces in \(\mathbb{R}^{K^2}\). While there is no
unique latent configuration \(X\) such that \(X X^\top = P\), the edge
probability \(P\) for the PABM, they all have this subspace structure,
and one in particular consists of \emph{orthogonal} subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent
configuration for a \(K\)-community PABM under the GRDPG framework
consists of vectors in \(\mathbb{R}^{K^2}\) such that each community
corresponds to a \(K\)-dimensional subspace and each subspace is
orthogonal to the others. However, because latent configurations are not
unique, we cannot apply this fact directly for community detection.

\begin{remark}
Let $A \sim \text{GRDPG}_{p, q}(Y)$. Then $A\sim \text{GRDPG}_{p, q}(Y Q)$ $\forall Q \in \mathbb{O}(p, q)$. This is because $Y Q I_{p, q} Q^\top Y^\top = Y I_{p, q} Y^\top$. 
\end{remark}

However, we can show that if we treat the rows of the eigenvectors of
\(P\) (ignoring the eigenvalues) as an embedding (unscaled ASE), then
they always form orthogonal subspaces. This is stated more formally in
Theorem \ref{osc}, and we call the resulting algorithm Orthogonal
Spectral Clustering.

### 2021-05-29 proposal/slides.Rmd
updated slides

---
title: Community Detection Methods for Generalized Random Dot Product Graphs
subtitle: Dissertation Proposal
author: John Koo
date: 'June 2021'
output: 
  beamer_presentation:
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: page_headers.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
---

@@

**Algorithm**: Sparse Subspace Clustering (Elhamifar and Vidal, 2009):

@@

```{r clust_err_k, fig.width = 10, fig.height = 3, out.width = '100%'}
setwd('~/dev/pabm-grdpg')
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(
    med.err = median(error),
    first.q = quantile(error, .25),
    third.q = quantile(error, .75),
    med.err.ssc = median(error.ssc),
    first.q.ssc = quantile(error.ssc, .25),
    third.q.ssc = quantile(error.ssc, .75),
    med.err.ep = median(error.ep, na.rm = TRUE),
    first.q.ep = quantile(error.ep, .25, na.rm = TRUE),
    third.q.ep = quantile(error.ep, .75, na.rm = TRUE),
    med.err.louvain = median(error.louvain),
    first.q.louvain = quantile(error.louvain, .25),
    third.q.louvain = quantile(error.louvain, .75)
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  scale_y_log10() +
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  # geom_line(aes(x = n, y = med.err.ep,
  #               colour = 'MM-EP')) + 
  # geom_errorbar(aes(x = n, ymin = first.q.ep, ymax = third.q.ep,
  #                   colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  geom_line(aes(x = n, y = med.err.louvain,
                colour = 'MM-Louvain')) + 
  geom_errorbar(aes(x = n, ymin = first.q.louvain, ymax = third.q.louvain,
                    colour = 'MM-Louvain'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

@@

@@

5. Explore the performance of these techniques in the presence of outliers.

6. Extend results to the GRDPG.

@@

>>>>

---
title: Community Detection Methods for Generalized Random Dot Product Graphs
subtitle: Dissertation Proposal
author: 
  - John Koo$^1$
  - Michael Trosset$^1$
  - Minh Tang$^2$
  - Julia Fukuyama$^1$
  - Roni Khardon$^3$
  - Fangzheng Xie$^1$
institute:
  - $^1$Indiana University, Department of Statistics
  - $^2$North Carolina State University, Department of Statistics
  - $^3$Indiana University, Department of Computer Science
date: 'June 2021'
output: 
  beamer_presentation:
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: page_headers.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
---

@@

**Algorithm**: Sparse Subspace Clustering (Elhamifar & Vidal, 2009):

@@

```{r clust_err_k, fig.width = 10, fig.height = 3, out.width = '100%'}
setwd('~/dev/pabm-grdpg')
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(
    med.err = median(error),
    first.q = quantile(error, .25),
    third.q = quantile(error, .75),
    med.err.ssc = median(error.ssc),
    first.q.ssc = quantile(error.ssc, .25),
    third.q.ssc = quantile(error.ssc, .75),
    med.err.ep = median(error.ep, na.rm = TRUE),
    first.q.ep = quantile(error.ep, .25, na.rm = TRUE),
    third.q.ep = quantile(error.ep, .75, na.rm = TRUE),
    med.err.louvain = median(error.louvain),
    first.q.louvain = quantile(error.louvain, .25),
    third.q.louvain = quantile(error.louvain, .75)
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  scale_y_log10() +
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  # geom_line(aes(x = n, y = med.err.ep,
  #               colour = 'MM-EP')) + 
  # geom_errorbar(aes(x = n, ymin = first.q.ep, ymax = third.q.ep,
  #                   colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  # geom_line(aes(x = n, y = med.err.louvain,
  #               colour = 'MM-Louvain')) + 
  # geom_errorbar(aes(x = n, ymin = first.q.louvain, ymax = third.q.louvain,
  #                   colour = 'MM-Louvain'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

@@

Examples:

1. $r = 1$ and each $\gamma_k$ is a point mass $\implies$ SBM
2. $r = 1$ and the range of each $\gamma_k$ is a segment from the origin to point $y_k$ with $\|y_k\| \leq 1$ $\implies$ DCBM
3. $r = K$ and the range of each $\gamma_k$ is the hyperplane of coordinates $x_{K (k-1) + 1}$ to $x_{k K}$ $\implies$ PABM

@@

5. Extend results to the GRDPG.

# Thank you

@@

1. Let $A^{(kl)}$ be the block of edges between communities $k$ and $l$. 
2. For each $k, l \in [K]$, do:
    i. Compute the SVD $A^{(kl)} = U \Sigma V^\top$.
    ii. Assign $u^{(kl)}$ and $v^{(kl)}$ as the first columns of $U$ and $V$. 
    Assign $\sigma^{(kl)} \leftarrow \Sigma_{11}^{1/2}$. 
    iii. Assign $\hat{\lambda}^{(kl)} \leftarrow \pm \sigma^{(kl)} u^{(kl)}$ and 
    $\hat{\lambda}^{(kl)} \leftarrow \pm \sigma^{(kl)} v^{(kl)}$.

$$\max_{k, l} \|\hat{\lambda}^{(kl)} - \lambda^{(kl)}\| =
O_P \Big( \frac{(\log n_k)^c}{\sqrt{n_k}} \Big)$$
